---
title: "Praesi"
author: "Luca Wirths"
date: "2023-05-23"
output: powerpoint_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Group6 - Model for Salary expectaions

A funny but interesting regressiontask for SBD3

By Abishan, Josua, Lars & Luca
on 30.05.2023


## Agenda

- Dataset
- Data exploration
- Feature selection
- ML's
- Our results
- Learnings
- Annex

## Dataset

```{r , echo=FALSE}
load("data_wage.RData")
data_wage <- data #copy of dataset
set.seed(8)
overview(data)
summary(data)
```

## Dataset Switzerland
```{r}
nrow(data_wage$country == "Switzerland"]

```



## Data exploration I 
```{r}
#Let's visualize the wage columnns with and without outliers
data %>%
  plot_outlier(col="aquamarine3",diagnose_outlier(data['wage']) %>%
                 filter(outliers_ratio >= 0.5) %>%          # dplyr
                 select(variables) %>%
                 unlist())
```

## Data Exploration II
10% outliers

```{r,echo=FALSE}


outlier <- function(x){
  quantiles <- quantile(x, c(.1, .9))
  x[x < quantiles[1]] <- quantiles[1]
  x[x > quantiles[2]] <- quantiles[2]
  x
}   
#Use function outlier for the dataset
data['wage'] <- map_df(data['wage'], outlier)

#Save to later use on 
data_outliers10 <- data
# Let's check our dependent variable "wage"
ggplot(data_outliers10, aes(x = wage)) + 
  geom_histogram(fill="aquamarine3", color = "black") +
  labs(title = "Histogram of the wages for option 1") +
  theme(legend.position="none")
```


## Data exploration III
data findings of students 150k, or employees with income 0
```{r, echo=FALSE}
# Check how many non-students have wage = 0 
num_rows_1 <- nrow(data[data$wage == 0 & !(data$job_role == "Student" | data$industry == "I am a student"), ])
print(paste("Number of **Non** student's, with wage 0:", num_rows_1))

# Check how many students have wage > 150'000
num_rows_2 <- nrow(data[data$wage > 150000 & (data$job_role == "Student" | data$industry == "I am a student"), ])
print(paste("Number of student's, with wage more than 150,000:", num_rows_2))

#remove non students with 0 income
data_remove <- data_wage[!(data_wage$wage == 0 & data_wage$job_role != "Student" | data_wage$wage == 0 & data_wage$industry != "I am a student"), ]

#remove students with income > 150k
data_remove <- data_remove[!(data_remove$wage > 150000 & (data_remove$job_role == "Student" | data_remove$industry == "I am a student")), ]

#create new outlierfunction 5/95%
outlier1 <- function(x){
  quantiles <- quantile(x, c(.05, .95))
  x[x < quantiles[1]] <- quantiles[1]
  x[x > quantiles[2]] <- quantiles[2]
  x
}   
#use outlierfunction
data_remove['wage'] <- map_df(data_remove['wage'], outlier1)

data_remove_n_outlier5 <- data_remove
# Let's check our dependent variable "wage"
ggplot(data_remove_n_outlier5, aes(x = wage)) + 
  geom_histogram(fill="aquamarine3", color = "black") +
  labs(title = "Histogram of the wages for option 2") +
  theme(legend.position="none")
```

## Feature selection I

Boruta output 1:

## Feature selection II

Boruta output 2:


## ML's I

Leaderboard Outliers 10
```{r}
lb <- automl@leaderboard
print(lb, n = nrow(lb)) 
```


## ML's II

Leaderboard Remove unlogical entries and outliers 5
```{r}
lb <- automl1@leaderboard
print(lb, n = nrow(lb)) 
```

## Abishans' result
```{r}
Abishan <- h2o.explain_row(best_RMSE, test, row_index = 1)
Abishan$shap_explain_row$plots
```

## Josua's result
```{r}
Josua <- h2o.explain_row(best_RMSE, test, row_index = 2)
Josua$shap_explain_row$plotsv
```

## Lars' result
```{r}
Lars <- h2o.explain_row(best_RMSE, test, row_index = 3)
Lars$shap_explain_row$plots
```

## Luca's result
```{r}
Luca <- h2o.explain_row(best_RMSE, test, row_index = 4)
Luca$shap_explain_row$plots
```

## Learnings 

- Systematic apporach is really important
- H2O Auto ML is a nice tool, which helps a lot.
- Dataentries questionable (think of the permutations of the teachers)
- The answers of a survey ar not that reliable, people could lie easily. ex. Luca did not feel as a student but everyone else did (they also work parttime)

## ANNEX
